---
title: "ttest.rjs Package: Realease v1.0"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Package: Progress 3}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Constructor, Print, and Plot Functions

**(*Not shown below*) Four helper functions:** <br>
**`is.number(x)`** checks not only if `x` is a numeric but also if it is a single number.<br>
**`is.string(x)`** checks if `x` contains characters and has a length of 1.<br>
**`is.stringORnull(x)`** performs `is.string(x)` and additionally checks if `x` is NULL.<br>
**`has.Rttest.data(x)`** Ensures the "data" variable is inside the Rttest object, `x`, is unaltered. Then returns that "data" for ease of use.<br>

``` {r source}
library(ttest.rjs)
ttest.rjs::Rttest
ttest.rjs:::print.Rttest
ttest.rjs:::plot.Rttest
```


## 3 Form Execution Test

Below are 3 types of tests that Rttest can preform depending on the variance of 
the samples and given input parameters: T-test, Welch, and Paired.
``` {r test, fig.align="center", fig.width=5, fig.height=4}
set.seed(32); x=rnorm(30,mean=10,sd=15)
set.seed(35); y=rnorm(30,mean=8,sd=15)
t_test = Rttest(x,y,alpha=0.05,paired=FALSE)
print(t_test)
plot(t_test)

set.seed(32); x=rnorm(30,mean=10,sd=5)
set.seed(35); y=rnorm(30,mean=8,sd=15)
welch=Rttest(x,y,alpha=0.05,paired=FALSE)
print(welch)
plot(welch)

set.seed(32); x=rnorm(30,mean=10,sd=15)
set.seed(35); y = x+ rnorm(30, 5 ,4)
paired=Rttest(x,y,alpha=0.05,paired=TRUE)
print(paired)
plot(paired)
```

## Print and Plot Extened functionality

The dimentionality of the `kable` output from the `print()` function can be sized 
to the users needs, and the labels of the `ggplot2` can be modified from the 
`plot()` function.
``` {r generics, fig.align="center", fig.width=5, fig.height=4}
print(t_test, T, 400, 200)
plot(t_test, main="My Custom Title", sub="Which also has a sub-title",
     poplab="My Population", vlab="My Value")
```

