---
title: "Package: Progress 4"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Package: Progress 3}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Constructor, Print, and Plot Functions

**(*Not shown below*) I have added 4 new helper functions:** <br>
**`is.number(x)`** checks not only if `x` is a numeric but also if it is a single number.<br>
**`is.string(x)`** checks if `x` contains characters and has a length of 1.<br>
**`is.stringORnull(x)`** performs `is.string(x)` and additionally checks if `x` is NULL.<br>
**`has.Rttest.data(x)`** Ensures the "data" variable is inside the Rttest object, `x`, is unaltered. Then returns that "data" for ease of use.<br><br>
I have also added several optional parameters to personalize the use-case of both print (adjusting the size of the kable output) and the plot functions (allowing the user to personalize the labels of the plot).

``` {r source}
ttest.rjs::Rttest
ttest.rjs:::print.Rttest
ttest.rjs:::plot.Rttest
```


## Execution Test

``` {r test, fig.align="center", fig.width=5, fig.height=4}
set.seed(21);x <-rnorm(30,5,2); set.seed(23); y<- rnorm(30, 3,2); alpha <- 0.05
obj <-ttest.rjs::Rttest(x=x,y=y,alpha = 0.05)
library(ttest.rjs)
print(obj)
plot(obj)
```
